---
title: "airbnb"
author: "Chicane"
date: "`r Sys.Date()`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, eval=F, comment=NA, message=F, warning=F)
library(dplyr)
library(MASS)
library(readr)
```

```{r}
airbnb = read.csv('/Users/cosmoser/Desktop/airbnb.csv')
head(airbnb)
airbnb = airbnb %>% 
  mutate(cancel_policy = as.factor(cancel_policy),
         neighbourhood = as.factor(neighbourhood),
         property_type = as.factor(property_type),
         room_type = as.factor(room_type),
         instant_bookable = as.factor(instant_bookable),
         superhost = as.factor(superhost),
         TV = as.factor(TV),
         AC= as.factor(AC),
         Parking = as.factor(Parking),
         Checkin_24hour = as.factor(Checkin_24hour),
         Pets_allowed = as.factor(Pets_allowed),
         Gym = as.factor(Gym),
         Pets_live = as.factor(Pets_live),
         Kid_friendly = as.factor(Kid_friendly)
)
summary(airbnb)
```
**Findings:** The max of $min_nights$ is 1000, which is not reasonable and can be regarded as outlier.

```{r}
par(mfrow=c(2,4))
Name=names(airbnb)
##airbnb$minimum_nights[minimum_nights = 1000] = 0
for(i in c(1:12)){
  hist(airbnb[,i], main=Name[i], xlab=Name[i])
  qqnorm(airbnb[,i], main=Name[i], xlab=Name[i])
  qqline(airbnb[,i])}
```
**Findings:** All variables are in skewed distribution.
```{r}
par(mfrow=c(2,4))
for (i in c(13:23, 26)){
  boxplot(airbnb$price~airbnb[,i], main=Name[i], xlab=Name[i])
}
```
```{r}
boxplot(airbnb$price~airbnb$neighbourhood, main=Name[24], xlab=Name[24])
boxplot(airbnb$price~airbnb$neighbourhood, main=Name[25], xlab=Name[25])
```
```{r}
par(mfrow=c(2,2))
for (i in c(2:12)) {
  lmod0=lm(I(abs(airbnb[,i])+0.001)~1)
  b=boxcox(lmod0,xlab=Name[i])
}
```
**Findings:** We need to transform all variables except host_response_rate and discrete ones.

```{r}
par(mfrow=c(2,2))
for (i in c(2:12)) {
  plot(airbnb[ , i], airbnb$price, main=Name[i], xlab=Name[i], ylab="price")
}
```
**Findings:** No predictors seem to have linear associations with the response variable $price$.

```{r}
lmod1 = lm(price~. ,data=airbnb)
summary(lmod1)
par(mfrow=c(2,2))
plot(lmod1)
boxcox(lmod1)
```
**Findings:** R-squared is 0.5386. Residual plot seems to appear close to random. QQplot is close to straightline. The leverage plot (bottom-right) shows to potential influential points (2485).

```{r}
lmod2=lm(I(price^(-1/5))~host_response+deposit+cleaning_fee+availability_90+review_num+review_score+guests_included+min_nights+bathrooms+bedrooms+beds+instant_bookable+TV+Parking+AC+Checkin_24hour+Pets_allowed+Gym+Pets_live+Kid_friendly+superhost+room_type+property_type+cancel_policy+neighbourhood,data=airbnb)
summary(lmod2)
par(mfrow=c(2,2))
plot(lmod2)
```
**Findings:** 
(1) The boxcox suggests a ^(-1/5)-transformation for the response variable $price$.
(2) The new model with transformed response variable has an improved R-squared around $0.7011$, whose diagnostic plots all look better than the previous.

```{r}
Name=names(airbnb)
par(mfrow=c(2,2))
for (i in c(2:12)) {
  plot(airbnb[ , i], (airbnb$price)^(-1/5), main=Name[i], xlab=Name[i], ylab="price^(-1/5)")
}
```
**Findings:** The linear relationship is still not obvious.

```{r}
airbnb$log.deposit = log(airbnb$deposit+0.001)
airbnb$t.cleaning_fee = airbnb$cleaning_fee^(0.2)
airbnb$t.availability_90 = airbnb$availability_90^(0.4)
airbnb$t.review_num = airbnb$review_num^(0.2)
airbnb$t.review_score = airbnb$review_score^2
Name = names(airbnb)
par(mfrow=c(2,2))
for (i in c(27:31)) {
  plot(airbnb[,i],(airbnb$price)^(-1/5),main=Name[i],xlab=Name[i],ylab="price^(-1/5)")
}
```
**Findings:** After transforming some continuous numerical variables, the relationship becomes more linear.

```{r}
lmod3 = lm(I((price)^(-1/5))~host_response+log.deposit+t.cleaning_fee+t.availability_90+t.review_num+t.review_score+guests_included+min_nights+bathrooms+bedrooms+beds+instant_bookable+TV+Parking+AC+Checkin_24hour+Pets_allowed+Gym+Pets_live+Kid_friendly+superhost+property_type+cancel_policy+room_type+neighbourhood, data=airbnb)
summary(lmod3)
par(mfrow=c(2,2))
plot(lmod3)
```
```{r}
studres=rstudent(lmod3)
range(studres)
out.idx = which(abs(studres)>3)
out.idx
length(out.idx)
```
**Findings:** There are 27 outliers in our data base.

```{r}
airbnb[c(out.idx),]
summary(airbnb)
```

```{r}
out.ind = c(out.idx,31)
airbnb = airbnb[-out.ind,]
airbnb[1055,]
airbnb = airbnb[-1055,]
lmod3.new = lm(I((price)^(-1/5))~host_response+log.deposit+t.cleaning_fee+t.availability_90+t.review_num+t.review_score+guests_included+min_nights+bathrooms+bedrooms+beds+instant_bookable+TV+Parking+AC+Checkin_24hour+Pets_allowed+Gym+Pets_live+Kid_friendly+superhost+property_type+cancel_policy+room_type+neighbourhood, data=airbnb)
summary(lmod3.new)
par(mfrow=c(2,2))
plot(lmod3.new)
```

```{r}
library(MASS)
lmod.aic = stepAIC(lmod3.new,direction="both",k=2,trace = F)
summary(lmod.aic)
n=dim(airbnb)[1]
lmod.bic = stepAIC(lmod3.new,direction="both",k=log(n),trace = F)
summary(lmod.bic)
AIC(lmod.aic)
AIC(lmod.bic)
BIC(lmod.aic)
BIC(lmod.bic)
```

```{r}
library(faraway)
vif(lmod.bic)
vif(lmod.aic)
par(mfrow=c(2,2))
plot(lmod.bic)
```
```{r}
summary(lmod.bic)
par(mfrow=c(2,2))
lmod_bic_new = lm(formula = I((price)^(-1/5)) ~ host_response + t.cleaning_fee + 
    t.availability_90 + t.review_score + guests_included + 
    bathrooms + bedrooms + beds + instant_bookable + TV + 
    Checkin_24hour + superhost + room_type + 
    neighbourhood + I((t.availability_90)^2) + I((t.review_score)^2), data = airbnb)
summary(lmod_bic_new)
plot(lmod_bic_new)
```




